### 2015-09-15 definition.tex
Improved text

%% Definitions: filesystem, path, commands
\section{Definitions}
\label{theorem:def}
\subsection{The filesystem}
We introduce some known notations on filesystems and paths.

A filesystem can be \emph{broken} (\(F=\ud\))
or it can be a function mapping whole paths to their
contents. The filesystem is broken if a command caused an error, for
example deleting a directory with files under it.

A \emph{path} is either empty (/), or a finite sequence of names
separated by \(\cdot\). The concatenation of paths \(\pi\) and
\(\varphi\) can be written as \(\pi\cdot\varphi\).
We write
\(\pi\preceq\gamma\) iff \(\pi\) is a prefix of \(\gamma\), i.e., if
\(\gamma=\pi\cdot\alpha\) for some path \(\alpha\) which might be
empty. We also write
\(\pi\prec\gamma\) if \(\pi\) is a proper prefix of \(\gamma\), that is,
\(\pi\preceq\gamma\) and \(\pi\ne\gamma\). If we refer to the contents of
path \(\pi\) in filesystem \(F\), we write simply \(F(\pi)\).

@@

In a filesystem, the contents of a path can be broken (\(F(\pi)=\ud\),
if the file or directory does not exist), they can be
a file (\(F(\pi)=\cfile{X}\)) or a directory (\(F(\pi)=\cdir{Y}\)).  
We also write \(X\) or \(Y\) for some unspecified but non-\(\ud\)
contents.
\begin{notrsi} 
Both files and directories can carry additional information
(modtimes, permissions, the bytes in a file, etc.), which we leave
unspecified, simply writing the contents as shown above.
\end{notrsi}

@@

We have some restrictions on filesystems: all filesystems must satisfy
the \emph{tree property}, that
is, if \(\pi\prec\gamma\) and \(F(\gamma)\neq\ud\) then
\(F(\pi)=\cdir{X}\). It means that every path which has a descendant must
be a directory.

@@

At first, we
thought about using four commands: \(create\), \(remove\), \(edit\) and
\(move\), as the most common commands on a filesystem. Later, \(move\)
turned out to be hard to handle in the algebra. We decided to introduce
this command only in the user interface, after running the synchronizer.
We also needed a command to reason about commands that cause errors
(\(break\)). So we took another set of commands; it consists of the
commands \(create\), \(remove\), \(edit\) and \(break\). In appendix
\ref{app:update-move} we provide an argument to justify using a
move--free
algebra.

\begin{notrsi}
All the commands have the following property: if applied to a filesystem,
then it either breaks the system (\(command(\pi,X)F=\ud\)) or 
\(command(\pi,X)F=F\{\pi\mapsto X\}\); that is, if a command does not
break the filesystem, it only affects the filesystem at the path on which
it was applied. 
\end{notrsi}

Now we define the exact behavior of each command.
%We have four commands: \emph{create, edit, remove} and \emph{break.} 
Applied to the broken filesystem, they all have the same effect:  leaving
the filesystem in the broken state. Otherwise, 
the definition of their effect is the following:

\begin{notrsi}
\begin{itemize}
\item
\(create(\pi,X)\) modifies \(F(\pi)\) to \(X\) iff
\(F(\pi)\) is broken and its parent is a directory; i.e.
\[create(\pi,X)F=
\begin{cases}
F\{\pi\mapsto X\}, &\mbox{iff~} F(\pi)=\ud
\wedge F(parent(\pi))=\cdir{Y}\\
\ud, &\mbox{otherwise.}
\end{cases}\]
\item
The command \(edit\) can change the type of a path (file or
directory), according to its second argument.
Since the tree--property must be preserved, the definition is:
\begin{align*}
edit(\pi,\cdir{X})F&=
\begin{cases}
F\{\pi\mapsto \cdir{X}\}, &\mbox{iff~}
F(\pi)\neq\ud\\
\ud &\mbox{otherwise;}
\end{cases}\\
edit(\pi,\cfile{X})F&=
\begin{cases}
F\{\pi\mapsto\cfile{X}\} &\mbox{iff~}
F(\pi)\neq\ud\wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}
\end{align*}
\item
\(remove(\pi)\) only removes files or directories without files:
\[remove(\pi)F=
\begin{cases}  
F\{\pi\mapsto\ud\} &\mbox{iff~}
F(\pi)\neq\ud \wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}\]
\item
\(break\) breaks the filesystem:
\[\begin{array}{r@{}ll}
breakF&{}=\ud &\mbox{for every $F$.}\end{array}\]
\end{itemize}
\end{notrsi}
%
\begin{forrsi}
{\small{
%\begin{align}
\begin{gather*}\begin{array}{r@{}ll}
create(\pi,X)F&{}=F\{\pi\mapsto X\}, 
&\mbox{iff~}(F(\pi)=\ud)\wedge(F(parent(\pi))=\cdir{Y})\\
&{}=\ud, &\mbox{otherwise.}\\
edit(\pi,\cdir{X})F&{}=F\{\pi\mapsto \cdir{X}\}, 
&\mbox{iff~}F(\pi)\neq\ud\\
&{}=\ud &\mbox{otherwise;}\\
edit(\pi,\cfile{X})F&{}=F\{\pi\mapsto\cfile{X}\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\  
&{}=\ud &\mbox{otherwise.}\\
remove(\pi)F&{}=F\{\pi\mapsto\ud\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\
&{}=\ud &\mbox{otherwise.}\\
breakF&{}=\ud &\mbox{for every $F$.}
\end{array}\end{gather*}
%\end{align}
}}
\end{forrsi}
%%%%%%%%%% TAGS!
We write \(\emptyseq\) for the empty sequence of commands.

>>>>

%% Definitions: filesystem, path, commands
\section{Definitions}
\label{theorem:def}
\subsection{The filesystem}
We introduce some notation on filesystems and paths.

A filesystem can be \emph{broken} (\(F=\ud\))
or it can be a function mapping whole paths to their
contents. The filesystem is broken if a command has caused an error, for
example attempted to delete a directory with files under it.

A \emph{path} is either empty (/), or is a finite sequence of names
separated by \(\cdot\). The concatenation of paths \(\pi\) and
\(\varphi\) can be written as \(\pi\cdot\varphi\).
We write
\(\pi\preceq\gamma\) iff \(\pi\) is a prefix of \(\gamma\), i.e., if
\(\gamma=\pi\cdot\alpha\) for some path \(\alpha\) which may be
empty. We also write
\(\pi\prec\gamma\) if \(\pi\) is a proper prefix of \(\gamma\), that is,
\(\pi\preceq\gamma\) and \(\pi\ne\gamma\). If we refer to the contents of
path \(\pi\) in filesystem \(F\), we simply write \(F(\pi)\).

@@

In a filesystem, the contents of a path can be broken (\(F(\pi)=\ud\),
if the file or directory does not exist), they can be
a file (\(F(\pi)=\cfile{X}\)) or a directory (\(F(\pi)=\cdir{Y}\)).  
We also write \(X\) or \(Y\) for some unspecified but non-\(\ud\)
contents.
\begin{notrsi} 
In real-life filesystems, files and directories can carry additional information
like modification times, permissions, etc.
Here we consider these included in the contents. 
\end{notrsi}

@@

All filesystems must satisfy
the \emph{tree property}, that
is, if \(F(\gamma)\neq\ud\) then for every \(\pi\) either
\(childless_F(\pi)\) or \(F(\pi)=\cdir{X}\).
This means that every path which has a descendant must
be a directory.

@@

At first, we
considered using four commands: \(create\), \(remove\), \(edit\) and
\(move\), as the most common commands on a filesystem. Later, \(move\)
turned out to be too complicated to handle in the algebra. We decided to introduce
this command only in the user interface, after running the synchronizer.
We also needed a command to reason about commands that cause errors
(\(break\)). So we took another set of commands; it consists of the
commands \(create\), \(remove\), \(edit\) and \(break\). In appendix
\ref{app:update-move} we provide an argument to justify using a
move--free
algebra.

\begin{notrsi}
All commands have the following property: if applied to a filesystem,
they either break the system (\(command(\pi,X)F=\ud\)) or 
\(command(\pi,X)F=F\{\pi\mapsto X\}\); that is, they only affect the filesystem at the path on which
they were applied. 
\end{notrsi}

Now we define the exact behavior of each command.
%We have four commands: \emph{create, edit, remove} and \emph{break.} 
Applied to the broken filesystem, they all leave
the filesystem in the broken state. Otherwise, 
the definition of their effect is as follows:

\begin{notrsi}
\begin{itemize}
\item
\(create(\pi,X)\) modifies \(F(\pi)\) to \(X\) iff
\(F(\pi)\) is broken and its parent is a directory; i.e.
\[create(\pi,X)F=
\begin{cases}
F\{\pi\mapsto X\}, &\mbox{iff~} F(\pi)=\ud
\wedge F(parent(\pi))=\cdir{Y}\\
\ud, &\mbox{otherwise.}
\end{cases}\]
\item
The command \(edit\) can change the type of a path (file or
directory) according to its second argument.
Since the tree property must be preserved, the definition is:
\begin{align*}
edit(\pi,\cdir{X})F&=
\begin{cases}
F\{\pi\mapsto \cdir{X}\}, &\mbox{iff~}
F(\pi)\neq\ud\\
\ud &\mbox{otherwise;}
\end{cases}\\
edit(\pi,\cfile{X})F&=
\begin{cases}
F\{\pi\mapsto\cfile{X}\} &\mbox{iff~}
F(\pi)\neq\ud\wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}
\end{align*}
\item
\(remove(\pi)\) only removes files or directories without files:
\[remove(\pi)F=
\begin{cases}  
F\{\pi\mapsto\ud\} &\mbox{iff~}
F(\pi)\neq\ud \wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}\]
\item
\(break\) breaks the filesystem:
\[\begin{array}{r@{}ll}
breakF&{}=\ud &\mbox{for every $F$.}\end{array}\]
\end{itemize}
\end{notrsi}
%
\begin{forrsi}
{\small{
%\begin{align}
\begin{gather*}\begin{array}{r@{}ll}
create(\pi,X)F&{}=F\{\pi\mapsto X\}, 
&\mbox{iff~}(F(\pi)=\ud)\wedge(F(parent(\pi))=\cdir{Y})\\
&{}=\ud, &\mbox{otherwise.}\\
edit(\pi,\cdir{X})F&{}=F\{\pi\mapsto \cdir{X}\}, 
&\mbox{iff~}F(\pi)\neq\ud\\
&{}=\ud &\mbox{otherwise;}\\
edit(\pi,\cfile{X})F&{}=F\{\pi\mapsto\cfile{X}\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\  
&{}=\ud &\mbox{otherwise.}\\
remove(\pi)F&{}=F\{\pi\mapsto\ud\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\
&{}=\ud &\mbox{otherwise.}\\
breakF&{}=\ud &\mbox{for every $F$.}
\end{array}\end{gather*}
%\end{align}
}}
\end{forrsi}
%%%%%%%%%% TAGS!
We write \(\emptyseq\) for the empty sequence of commands.

### 2015-09-15 theorems.tex
Improved text

For sequences \(S_1\) and \(S_2\), we have two kinds of judgements:
\begin{itemize}
\item \(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
\(S_2\)}. Its intended interpretation is that they act the same on all
filesystems, i.e. \(\forall F: S_1F=S_2F\).
\item \(S_1\eqexp S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
interpretation is the following: if \(S_1\eqexp S_2\) and 
\(S_1F\ne\ud\) then \(S_1F=S_2F\).
%%%
%%% Transitivity? == => =C ?
%%%
\end{itemize}

@@

\begin{notrsi}
\medskip
{\small{
How many pairs do we have? 
For the first group of laws which contain a pair of commands from
\(edit\), \(create\) and \(remove\), we can choose a pair 9 ways.
We have four types of
path-pairs: \(\pi;\pi\), \(\pisub;\pi\), \(\pi;\pisub\)
and \(\pi;\varphi\). That makes \(4\times9\) cases. With \(break\), we have
\(3\times 2\) cases
with an other non--break command (there are 3 types and they can follow
or precede \(break\)) and one case when we have a pair made of two
\(break\)s. Thus, we have \(4\times 9+3\times2+1=43\) pairs. 
}}
\medskip
\end{notrsi}

We subdivide some laws containing \(edit\) because of \(edit\)'s different
behavior when modifying paths to files or to directories. These laws are
numbered with A or B.
Extension laws (that is, where the relation is \(\eqexp\), not
\(\equiv\)) are marked with \(E\).
%%%
%%% reference
%%%
(See table 1 for the laws.)

@@

An inference rule makes it possible to derive new statements from 
statements already true or from the axioms. 
Our inference rules are:\\
\emph{For any sequences \(S_1, S_2, S, S'\):}
\begin{itemize}
\item if \(S_1\equiv S_2\) then \(S;S_1;S'\equiv S;S_2;S'\)
\item if \(S_1\eqexp S_2\) then \(S;S_1;S'\eqexp S;S_2;S'\)
\item if \(S_1\equiv S_2\) then \(S_1\eqexp S_2\).
\end{itemize}
As we can see, the first inference rules are mere substitutions of a part
of the sequence to another sequence. 
%%\remark{``...'' is only for app. \ref{app:theosound}}
If ``\(S_1\equiv S_2\)'' or 
``\(S_1\eqexp S_2\)'' is a law itself, we say that we applied that law to
the sequence \(S;S_1;S'\).

\subsection{Soundness theorem}
\label{theorem:soundness}
In order to be able to use our algebra,
we must show that algebraic relation between sequences also means
that the sequences act the same on filesystems.
%
It can be proven that for every two sequences of commands 
\begin{gather*}
S\equiv S^* \implies \forall F: SF=S^*F,\\
(S\eqexp S^*)\wedge(SF\ne\ud)\implies \forall F: SF=S^*F.%\\
%S\eqifnbr S^*\wedge SF\ne\ud \wedge S^*F\ne\ud 
%\implies \forall F: SF=S^*F.
\end{gather*}
%%%\begin{forrsi}
The proof for the two cases are very similar. We use induction on the
number of times the inference rules were applied to the sequences. 
We obtain these results by
showing the soundness of each individual law (which can be done by
investigating numerous cases) and the inference rules.

The detailed proof can be found in Appendix \ref{app:theosound}.
%%%\end{forrsi}
%%%\begin{notrsi}
%%%\input{sound}
%%%\end{notrsi}

@@

Let us introduce some notation. We write 
\(S_1\eqifnbr S_2\), or \emph{\(S_1\) and \(S_2\) have a common upper 
bound} iff
\(\exists S^*: S_1\eqexp S^* \wedge S_2\eqexp S^*\), that is, iff
both \(S_1\) and \(S_2\) can be extended to the same sequence.
It is a symmetric relation, but not transitive.

\(S_1\equiv S_2\implies S_1\eqexp S_2\implies S_1\eqifnbr S_2\) also
holds.

%To show that we have enough laws to describe the algebra of
%filesystems,
Now we prove that if 
two sequences of commands act the same on any filesystem neither of
them breaks, \emph{and} there is a filesystem neither of them
breaks then they have a common upper bound.
Formally, 
\[\begin{array}{r@{}l}
\forall S,S':&\\ 
&((\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
&\wedge\\
&(\exists F: SF\ne\ud\wedge S'F\ne\ud)\\
&\implies S \eqifnbr S'),
\end{array}\]
where \(G\) and \(F\) refer to filesystems.

%%%\begin{notrsi}
%%%\input{compl}
%%%\end{notrsi}
%%%\begin{forrsi}

In the proof we define \emph{minimal sequences} in the following way:
Consider the set of sequences \(\wp_S = \{ S^* | S \eqexp S^*\}\).
Because of our preconditions, the sequence \(break\) is not in
\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(SF=\ud\) would hold
since by definition \(SF=(break)F\) if \(SF\ne\ud\)).

Let \(S_0\) be (one of) the shortest sequence(s) in \(\wp_S\) and
similarly
\(S^\prime_0\) (one of) the shortest sequence(s) in \(\wp_{S^\prime}\). 
These sequences are called minimal sequences. It can be shown that for
every \(G\) which satisfies the condition \(SG\ne\ud\wedge S'G\ne\ud\), 
\(S_0G=S'_0G\ne\ud\) applies.
As a special case, we know that \(S_0F=S'_0F\ne\ud\).

The proof has three main steps.
\begin{itemize}
\item[i.]
We have some constraints on \(S_0\) and \(S'_0\). Since they do not break
every filesystem, no breaking laws can be applied to them. And since
they have minimal length, we cannot apply a simplifying law either. From
these properties we can prove that there is at most one command on each
path in a minimal sequence. (If there were more, such a law would
be appliable.)
\item[ii.]
We know that a command on path \(\pi\) only affects the filesystem at
\(\pi\) if it does not break the filesystem. Therefore \(S_0\) and
\(S'_0\) must contain commands on the same paths since
they do not break \(F\) and \(S_0F=S'_0F\), so they modify \(F\) at 
the same points. 
And we can also prove that the sequences must contain the same
commands on each path from the fact that they act the same on every \(G\).
Therefore they consist of the very same commands.
\item[iii.]
We prove that \(S_0\) and \(S'_0\) can be reordered by commuting
laws so that they would be the same sequences. That is, a sequence
\(S^*\) exists for which \(S_0\eqexp S^*\eqshr S'_0\). It means that
\(S\eqexp S_0\eqexp S^*\eqshr S'_0\eqshr S'\), i.e. \(S\eqifnbr S'\).
\end{itemize}

@@

\medskip
Now, since we know that our algebra is sound and complete for its
intended interpretation, we can use it to define the specification of the
file synchronizer.
%%%\end{forrsi}

>>>>

For sequences \(S_1\) and \(S_2\), we have two kinds of judgements:
\begin{itemize}
\item \(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
\(S_2\)}. Its intended interpretation is that they act the same on all
filesystems, i.e. \(\forall F: S_1F=S_2F\).
\item \(S_1\eqexp S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
interpretation is that if \(S_1\) does not break a filesystem, then they act
the same on it, i.e. \(\forall F: S_1F\ne\ud \implies S_1F=S_2F\).
%%%
%%% Transitivity? == => =C ?
%%%
\end{itemize}

@@

\begin{notrsi}
\medskip
{\small{
How many pairs do we have? 
From
\(edit\), \(create\) and \(remove\), we can choose a pair in 9 ways.
Moreover, there are four types of
path-pairs: equivalence \(\pi;\pi\), subordination \(\pisub;\pi\),
superordination \(\pi;\pisub\)
and incomparable paths \(\pi;\varphi\). These make \(4\times9\) cases. With \(break\), we have
\(3\times 2\) additional cases
with another non--break command (there are 3 types and they can follow
or precede \(break\)), and one case when we have a pair made of two
\(break\)s. Thus, we have \(4\times 9+3\times2+1=43\) pairs. 
}}
\medskip
\end{notrsi}

We subdivide some laws containing \(edit\) because of \(edit\)'s different
behavior when modifying paths to files or to directories. These laws are
numbered with A or B.
Extension laws (that is, where the relation is \(\eqexp\), not
\(\equiv\)) are marked with \(E\).
%%%
%%% reference
%%%
% (See table 1 for the laws.)

@@

An inference rule makes it possible to derive new statements from 
the axioms or from statements already known to be true. 
The inference rules are:\\
\emph{For any sequences \(S_1, S_2, S, S'\):}
\begin{itemize}
\item if \(S_1\equiv S_2\) then \(S;S_1;S'\equiv S;S_2;S'\)
\item if \(S_1\eqexp S_2\) then \(S;S_1;S'\eqexp S;S_2;S'\)
\item if \(S_1\equiv S_2\) then \(S_1\eqexp S_2\).
\end{itemize}
Te first two inference rules merely substitute part of a sequence for
another sequence.
If ``\(S_1\equiv S_2\)'' or 
``\(S_1\eqexp S_2\)'' is a law, we say that we applied that law to
the sequence \(S;S_1;S'\).

\subsection{Soundness theorem}
\label{theorem:soundness}
In order to be able to use our algebra,
we must show that an algebraic relation between sequences also means
that the sequences act the same on filesystems.
%
It can be proven that for every two sequences of commands
\(S\) and \(S^*\) 
\begin{gather*}
\forall F: S\equiv S^* \implies SF=S^*F,\\
\forall F: (S\eqexp S^*)\wedge(SF\ne\ud)\implies SF=S^*F.
\end{gather*}
The proofs for the two cases are very similar. We use induction on the
number of times the inference rules are applied to the sequences.
The soundness of each individual law
(by investigating individual cases)
and that of the inference rules are shown separately.
For the detailed proof see Appendix \ref{app:theosound}.

@@

Let us introduce some notation. We write 
\(S_1\eqifnbr S_2\), or \emph{\(S_1\) and \(S_2\) have a common upper 
bound} iff
\(\exists S^*: S_1\eqexp S^* \wedge S_2\eqexp S^*\), that is, iff
both \(S_1\) and \(S_2\) can be extended to the same sequence.
It is a symmetric relation, but not transitive.
\(S_1\equiv S_2\implies S_1\eqexp S_2\implies S_1\eqifnbr S_2\) also
holds.

Now we prove that if 
two sequences of commands act the same on any filesystem neither of
them breaks, \emph{and} there is a filesystem neither of them
breaks, then they are also related algebraically; namely, they have a common upper bound.
Formally, 
\[\begin{array}{r@{}l}
\forall S,S':&\\ 
&(\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
&\wedge\\
&(\exists F: SF\ne\ud\wedge S'F\ne\ud)\\
&\implies S \eqifnbr S',
\end{array}\]
where \(G\) and \(F\) refer to filesystems.

In the proof we define \emph{minimal sequences} in the following way:
Consider the set of sequences \(\wp_S = \{ S^* | S \eqexp S^*\}\).
Because of our preconditions, the sequence \(break\) is not in
\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(\forall F:SF=\ud\) would hold
by definition).

Let \(S_0\) be (one of) the shortest sequence(s) in \(\wp_S\) and
similarly
\(S^\prime_0\) (one of) the shortest sequence(s) in \(\wp_{S^\prime}\). 
We will call these minimal sequences. It can be shown that for
every \(G\) which satisfies the condition \(SG\ne\ud\wedge S'G\ne\ud\), 
\(S_0G=S'_0G\ne\ud\) applies.
As a special case, we know that \(S_0F=S'_0F\ne\ud\) where \(F\) is the
fileystem from the formalization of the theorem above.

The proof has three main steps.
\begin{itemize}
\item[i.]
We have some constraints on \(S_0\) and \(S'_0\). Since they do not break
every filesystem, no breaking laws can be applied to them. And since
they have minimal length, we cannot apply a simplifying law either. From
these properties we can prove that there is at most one command on each
path in a minimal sequence. (If there were more, a breaking or simplifying law
could be applied.)
\item[ii.]
We know that a command on path \(\pi\) only affects the filesystem at
\(\pi\) if it does not break the filesystem. Therefore \(S_0\) and
\(S'_0\) must contain commands on the same paths since
they do not break \(F\) and \(S_0F=S'_0F\), that is, they modify \(F\) at 
the same points. 
And we can also prove that the sequences must contain the same
commands on each path from the fact that they act the same on every \(G\).
Therefore they consist of the very same commands.
\item[iii.]
We prove that \(S_0\) and \(S'_0\) can be reordered using commuting
laws so that they would be the same sequences. That is, a sequence
\(S^*\) exists for which \(S_0\eqexp S^*\eqshr S'_0\). It means that
\(S\eqexp S_0\eqexp S^*\eqshr S'_0\eqshr S'\), i.e. \(S\eqifnbr S'\).
\end{itemize}

@@

\medskip
Now, since we know that our algebra is sound and complete for its
intended interpretation, we can use it to define the specification of the
file synchronizer.
